Signed-Rank Test

### 2024-03-19 examples/1a_Examples_DifferenceScores_PairedTtests.qmd
example updates

### Config Options

::: blue
**This code configures knitr code chunk options**

```{r config}
#| echo: TRUE
#| messages: FALSE
#| warning: FALSE
#| output: FALSE

knitr::opts_chunk$set(
    echo = T, message = F, warning = F, error = F,
    comment = NA, cache = T, code_folding = T,
    R.options = list(width = 220, digits = 3),
    fig.align = "center",
    out.width = "75%", fig.asp = .75
)
```
:::
:::

>>>>

```{r config}
#| echo: FALSE
#| messages: FALSE
#| warning: FALSE
#| output: FALSE

### Config Options
#::: blue
#**This code configures knitr code chunk options**

knitr::opts_chunk$set(
    echo = T, message = F, warning = F, error = F,
    comment = NA, cache = T, code_folding = T,
    R.options = list(width = 220, digits = 3),
    fig.align = "center",
    out.width = "75%", fig.asp = .75
)
```
:::

### 2024-03-19 examples/1b_Examples_DifferenceScores_SimpleRegression.qmd
example updates

### Config Options

::: blue
**This code configures knitr code chunk options**

```{r config}
#| echo: TRUE
#| messages: FALSE
#| warning: FALSE
#| output: FALSE

knitr::opts_chunk$set(echo = T, message=F, warning=F, error=F, 
                      comment=NA, cache=T, code_folding=T,
                      R.options=list(width=220, digits = 3),
                      fig.align='center', 
                      out.width='75%', fig.asp=.75)
```
:::
:::

>>>>

```{r config}
#| echo: FALSE
#| messages: FALSE
#| warning: FALSE
#| output: FALSE

### Config Options
#::: blue
#**This code configures knitr code chunk options**

knitr::opts_chunk$set(echo = T, message=F, warning=F, error=F, 
                      comment=NA, cache=T, code_folding=T,
                      R.options=list(width=220, digits = 3),
                      fig.align='center', 
                      out.width='75%', fig.asp=.75)
```
:::

### 2024-03-19 examples/4_Examples_SignedRankTest.qmd
updates
example updates

####
It is actually quite common that numeric depend variables need to be transformed or converted into ranks, i.e. ordinal variables, because the distribution of residuals does not allow the application of parametric tests such as t-tests or linear regression. In such cases, as we are dealing with rank (ordinal) data, the application of a chi-square test is unwarranted and we need to use another test. There are different alternatives depending on whether the data are paired (coming from the same individuals) or if all observations are independent.

@@

The code fits a xxxx to examine the 'xxxxx' variable across time points ('eventname'). It incorporates xxxxxx. The results of the model are then printed to provide a detailed summary of the fitted model parameters.

@@

>>>>

It is actually quite common that numeric depend variables need to be transformed or converted into ranks, i.e. ordinal variables, because the distribution of residuals does not allow the application of parametric tests such as t-tests or linear regression. In such cases, as we are dealing with rank (ordinal) data, the application of a chi-square test is unwarranted and we need to use another test. There are different alternatives depending on whether the data are paired (coming from the same individuals) or if all observations are independent.

@@

::: blue
The code fits a xxxx to examine the 'xxxxx' variable across time points ('eventname'). It incorporates xxxxxx. The results of the model are then printed to provide a detailed summary of the fitted model parameters.

@@

:::

### Model Plots

::: blue
Testtesttest

## Wrapping Up
<div class = "blue">

::: panel-tabset
### Write-up {.tabset .tabset-fade .tabset-pills}
